\documentclass[10pt, letterpaper]{article}
\usepackage[margin=0.75in]{geometry}
\usepackage{hyperref}

% --- Manual Section Formatting (Instead of titlesec) ---
\newcommand{\mysection}[1]{%
    \vspace{1.5ex}
    {\large\bfseries\uppercase{#1}}
    \vspace{0.5ex}
    \hrule
    \vspace{1ex}
}

% Remove page numbers
\pagestyle{empty}

\begin{document}

% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = 
% HEADER
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = 
\begin{center}
    {\Huge \textbf{VIJAYA GOPINADH REDDY VELAGALA}} \\ \vspace{2pt}
    \textbf{SENIOR DATA ENGINEER | SPECIALIST PROGRAMMER L2} \\ \vspace{4pt}
    Hyderabad, India | +91 6281762528 | \href{mailto:opportunities@thedevelopers.work}{opportunities@thedevelopers.work} \\ \vspace{2pt}
    \href{https://linkedin.com/in/thedeveloperswork}{linkedin.com/in/thedeveloperswork} | \href{https://github.com/thedeveloperswork}{github.com/thedeveloperswork} | \href{https://thedevelopers.work}{thedevelopers.work}
\end{center}

% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = 
% SUMMARY
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = 
\mysection{Summary}
\noindent Multidisciplinary \textbf{Senior Data Engineer} with over 4 years of experience architecting fault-tolerant, petabyte-scale distributed systems. Expert in \textbf{PySpark, Databricks, and AWS/Azure} serverless infrastructure. Specialized in deploying Medallion Lakehouse architectures, Write-Audit-Publish (WAP) validation patterns, and reducing compute latency by 30--60\%. Proven track record of ensuring 100\% data integrity and environment parity in mission-critical enterprise environments.

% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = 
% TECHNICAL ARSENAL
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = 
\mysection{Technical Arsenal}
\begin{itemize}
    \item \textbf{Data Processing \& Compute:} PySpark, Apache Spark, Databricks, Delta Lake, dbt, Flink, AWS Glue.
    \item \textbf{Cloud Ecosystem:} \textbf{AWS} (Step Functions, Lambda, CloudFormation, S3, Aurora), \textbf{Azure} (Data Factory, Synapse, Event Hubs, CosmosDB), \textbf{GCP} (Vertex AI, Gemini).
    \item \textbf{Languages:} Python, SQL, C++, C\#, JavaScript (Node.js, React.js).
    \item \textbf{Architecture:} Medallion (Bronze/Silver/Gold), Write-Audit-Publish (WAP), Z-Ordering, Salted Joins, Microservices, MVC.
    \item \textbf{DevOps \& Testing:} CI/CD (GitHub Actions), Docker, Pytest, Automated Validation Frameworks.
\end{itemize}

% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = 
% EXPERIENCE
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = 
\mysection{Experience}

\noindent \textbf{Infosys} \hfill NOV 2020 -- PRESENT \\
\textit{Specialist Programmer L2} \hfill Hyderabad, India
\begin{itemize}
    \item \textbf{Client: British Petroleum (Feb 2025 -- Present):}
        \begin{itemize}
            \item Engineered an automated Pytest-driven validation framework within CI/CD pipelines, eliminating manual SQL checks and achieving a 0\% defect injection rate.
            \item Architected serverless PySpark ETL pipelines utilizing AWS Glue and Step Functions, reducing execution time by 30\% for multi-terabyte datasets.
            \item Standardized infrastructure deployments using AWS CloudFormation, ensuring 100\% environment parity across Dev, Staging, and Prod.
        \end{itemize}
    \item \textbf{Client: Telstra (Mar 2021 -- Dec 2024):}
        \begin{itemize}
            \item Optimized Databricks-to-Synapse reads via pushdown predicates, slashing ADF pipeline execution time by 60\% (2 hours to 45 minutes).
            \item Led migration to Databricks Runtime 13.3 LTS within a B2B Medallion architecture, engineering source-to-target reconciliation for TB-scale data.
            \item Pioneered Write-Audit-Publish (WAP) architecture for enterprise data lakes, preventing downstream data corruption.
        \end{itemize}
    \item \textbf{Digital Specialist Engineer (Nov 2020 -- Feb 2021):}
        \begin{itemize}
            \item Designed data-driven solutions leveraging Azure Cloud and PySpark, earning Team MVP recognition for problem-solving.
        \end{itemize}
\end{itemize}

\vspace{4pt}

\noindent \textbf{Developers@Work} \hfill JAN 2018 -- FEB 2021 \\
\textit{Freelance Software Engineer} \hfill Remote
\begin{itemize}
    \item Executed full-stack architectures (ReactJS, NodeJS, Firebase) for diverse client portfolios and directed technical community building.
\end{itemize}

\vspace{4pt}

\noindent \textbf{KK Consultancy} \hfill MAY 2018 -- FEB 2021 \\
\textit{Full-Stack Developer Intern} \hfill Remote
\begin{itemize}
    \item Built reusable Auth/AuthZ middleware with JWT and Firebase authentication modules for full-stack web automation.
\end{itemize}

% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = 
% TECHNICAL PROJECTS
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = 
\mysection{Technical Projects}

\noindent \textbf{Retail360 Enterprise Lakehouse} \hfill \textit{Databricks, Delta Lake, PySpark} \\
\begin{itemize}
    \item Designed a production-grade Medallion Lakehouse architecture, decreasing query latency by 40\% via Z-Ordering and Data Skipping.
    \item Mitigated data skew using Salted Join strategies in PySpark, ensuring stable pipeline execution and preventing OOM errors.
\end{itemize}

\vspace{2pt}

\noindent \textbf{Eggventure 3D (FPS Simulation)} \hfill \textit{C++, C\#, Unity}
\begin{itemize}
    \item Engineered an Object Pooling system for 60+ FPS stability; built scalable game logic via State Machine AI and MVC patterns.
\end{itemize}

% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = 
% EDUCATION
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = 
\mysection{Education}

\noindent \textbf{Bachelor of Technology (Computer Science \& Engineering)} \hfill JUL 2016 -- SEP 2020 \\
Sasi Institute of Technology \& Engineering (JNTUK) \hfill CGPA: 7.63/10

\vspace{4pt}

\noindent \textbf{12th / Intermediate (MPC)} \hfill JUN 2014 -- APR 2016 \\
Adity Jr. College, Tadepalligudem (Board of Intermediate Education, AP) \hfill Score: 774/1000

\vspace{4pt}

\noindent \textbf{10th / SSC} \hfill JUN 2013 -- APR 2014 \\
St. Mary's English Medium High School, Prathipadu (Board of Secondary Education, AP) \hfill CGPA: 6.9/10

% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = 
% CERTIFICATIONS
% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = 
\mysection{Certifications}
\begin{itemize}
    \item \textbf{Microsoft:} Azure Data Engineer Associate | \textbf{Google Cloud:} Generative AI Leader
    \item \textbf{AWS:} Certified Solutions Architect Associate | \textbf{Infosys:} Certified Software Programmer
    \item \textbf{HackerRank:} SQL, Python, Java, Node, React, JavaScript (Core Accreditations)
\end{itemize}

\end{document}
