\documentclass[10pt, letterpaper]{article}
\usepackage[margin=0.75in]{geometry}
\usepackage{enumitem}
\usepackage{bookmark}
\usepackage{hyperref}
\usepackage{titlesec}

% --- Formatting Sections ---
\titleformat{\section}{\large\bfseries\uppercase}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{1ex}{1ex}

% Remove page numbers
\pagestyle{empty}

\begin{document}

% ==========================================
% HEADER
% ==========================================
\begin{center}
    {\Huge \textbf{VIJAYA GOPINADH REDDY VELAGALA}} \\ \vspace{2pt}
    \textbf{SENIOR DATA ENGINEER} \\ \vspace{4pt}
    Hyderabad, India | +91 6281762528 | opportunities@thedevelopers.work \\ \vspace{2pt}
    \href{https://linkedin.com/in/thedeveloperswork}{linkedin.com/in/thedeveloperswork} | \href{https://github.com/thedeveloperswork}{github.com/thedeveloperswork} | \href{https://thedevelopers.work}{thedevelopers.work}
\end{center}

% ==========================================
% SUMMARY
% ==========================================
\section{Summary}
\noindent Multidisciplinary Senior Data Engineer with 5+ years of experience architecting fault-tolerant, petabyte-scale distributed systems. Uniquely bridges the gap between low-level systems programming (C++/Unity) and modern Data Engineering (PySpark/Databricks). Specialized in deploying Medallion Lakehouse architectures, Write-Audit-Publish (WAP) validation patterns, and serverless cloud ecosystems (AWS/Azure). Proven track record of leveraging robust software engineering principles—such as microservices, state management, and CI/CD automation—to slash compute latency and guarantee 100\% data integrity in enterprise environments.

% ==========================================
% TECHNICAL ARSENAL
% ==========================================
\section{Technical Arsenal}
\begin{itemize}[leftmargin=0.15in, label={}]
    \item \textbf{Data Processing \& Compute:} PySpark [Active | 2025], Apache Spark [Active], Databricks (Delta Lake) [Dec 2024], Flink [2024]
    \item \textbf{Cloud Ecosystem (AWS \& Azure):} AWS (Glue, Step Functions, CloudFormation, S3) [Active], Azure (Data Factory, Synapse, CosmosDB, Event Hubs) [Dec 2024]
    \item \textbf{Architecture \& Patterns:} Medallion Lakehouse [Active], Write-Audit-Publish (WAP) Pattern [Active], High/Low-Level System Design [Active], Z-Ordering \& Data Skipping [2024], Design Patterns (MVC, Observer) [2023]
    \item \textbf{DevOps, Testing \& Infrastructure:} Pytest [Active], CI/CD (GitHub Actions, Azure DevOps) [Active], Infrastructure-as-Code (CloudFormation, Terraform) [Active], Docker \& Git [Active]
    \item \textbf{Foundational Programming:} Python, SQL [Active]
\end{itemize}

% ==========================================
% EXPERIENCE
% ==========================================
\section{Experience}

\noindent \textbf{Infosys (Client: British Petroleum)} \hfill Feb 2025 -- Present \\
\textit{Specialist Programmer L2 | Senior Data Engineer} \hfill Hyderabad, India
\begin{itemize}[leftmargin=0.25in, itemsep=1pt]
    \item Achieved a 0\% defect injection rate for mission-critical reference data, validated by the elimination of manual SQL checks, by engineering an automated Pytest-driven validation framework within CI/CD pipelines.
    \item Slashed execution time by 30\% for multi-terabyte datasets, benchmarked by pipeline performance metrics, by architecting serverless PySpark ETL pipelines utilizing AWS Glue and Step Functions.
    \item Secured 100\% environment parity across global regions, quantified by consistent deployment success rates, by standardizing infrastructure deployments using AWS CloudFormation.
\end{itemize}

\vspace{4pt}

\noindent \textbf{Infosys (Client: Telstra)} \hfill Mar 2021 -- Dec 2024 \\
\textit{Specialist Programmer L1 | Data Engineer} \hfill Hyderabad, India
\begin{itemize}[leftmargin=0.25in, itemsep=1pt]
    \item Accelerated Azure Data Factory (ADF) pipeline execution time by over 60\% (from 2 hours to 45 minutes), assessed by daily workload runtimes, by optimizing Databricks-to-Synapse reads via pushdown predicates and network bottleneck mitigation.
    \item Orchestrated the seamless processing of TB-scale data, validated by robust source-to-target reconciliation checks, by leading the migration of legacy ingestion workflows to Databricks Runtime 13.3 LTS within a B2B Medallion architecture.
    \item Pioneered guaranteed downstream data integrity, benchmarked by a sustained 0\% defect rate, by building the Write-Audit-Publish (WAP) architecture for enterprise data lakes.
    \item Boosted analytical query performance by 40\%, quantified by reporting latency, by integrating Azure Event Hubs and applying Z-Ordering on Gold-layer tables.
\end{itemize}

\vspace{4pt}

\noindent \textbf{Infosys} \hfill Nov 2020 -- Feb 2021 \\
\textit{Digital Specialist Engineer} \hfill Hyderabad, India
\begin{itemize}[leftmargin=0.25in, itemsep=1pt]
    \item Earned Team MVP recognition for problem-solving, validated by internal performance awards, by designing data-driven solutions leveraging Azure Cloud and PySpark.
    \item Mastered core Big Data technologies, assessed by successful enterprise training completion, by gaining proficiency in Hadoop, Spark, and Hive.
\end{itemize}

% ==========================================
% TECHNICAL PROJECTS
% ==========================================
\section{Technical Projects}

\noindent \textbf{Retail360 Enterprise Lakehouse} \hfill \textit{Databricks, Delta Lake, PySpark} \\
\textit{Repo: \href{https://github.com/DevelopersWork-Labs/data-engineering-portfolio-2026/tree/main/projects/01_lakehouse}{github.com/DevelopersWork-Labs/data-engineering-portfolio-2026/.../01\_lakehouse}}
\begin{itemize}[leftmargin=0.25in, itemsep=1pt]
    \item Designed enterprise analytical workloads, validated by successful production readiness, by deploying a Medallion Lakehouse architecture (Bronze/Silver/Gold).
    \item Decreased analytical query latency by $\sim$40\%, benchmarked by query execution, by implementing advanced Z-Ordering and Data Skipping techniques on Delta tables.
    \item Prevented out-of-memory (OOM) errors in high-volume distributed joins, quantified by stable pipeline execution, by engineering Salted Join strategies in PySpark to mitigate data skew.
    \item Guaranteed downstream data integrity, assessed by the prevention of schema drift, by establishing a Write-Audit-Publish (WAP) validation pattern.
\end{itemize}

\vspace{2pt}

\noindent \textbf{Evolved Pattern Matching (Rabin-Karp)} \hfill \textit{Python} \\
\textit{Repo: \href{https://github.com/thedeveloperswork/Evolved-Pattern-Matching-Rabin-Karp-Algorithm}{github.com/thedeveloperswork/Evolved-Pattern-Matching-Rabin-Karp-Algorithm}}
\begin{itemize}[leftmargin=0.25in, itemsep=1pt]
    \item Eliminated spurious hits, assessed by precise remainder and quotient equivalence, by modifying the traditional Rabin-Karp algorithm.
    \item Evaluated accelerated pattern matching over huge text sequences, quantified by reduced search latency, by deploying the optimized algorithm in a modular Python driver script.
\end{itemize}

\vspace{2pt}

\noindent \textbf{Movie Recommendation System} \hfill \textit{Python, ML} \\
\textit{Repo: \href{https://github.com/thedeveloperswork/Movie-Recommendation-System-using-Kmeans-and-Navie-Bayes}{github.com/thedeveloperswork/Movie-Recommendation-System-using-Kmeans-and-Navie-Bayes}}
\begin{itemize}[leftmargin=0.25in, itemsep=1pt]
    \item Improved user engagement, validated by the accuracy of content suggestions, by programming a recommendation engine based on user watch history.
    \item Formulated reliable Naive-Bayes classification, benchmarked by structured training models, by applying K-Means clustering on unsupervised datasets.
\end{itemize}

% ==========================================
% EDUCATION \& CERTIFICATIONS
% ==========================================
\section{Education \& Certifications}
\noindent \textbf{B.Tech in Computer Science \& Engineering} | Sasi Institute of Technology \& Engineering (JNTUK) \hfill 2016 -- 2020 \\
\textbf{Microsoft:} Azure Data Engineer Associate \\
\textbf{AWS:} Certified Solutions Architect Associate SAA-C03 \\
\textbf{Databricks:} Databricks Certified Data Engineer Prep \\
\textbf{Google Cloud:} Generative AI Leader \\
\textbf{Professional Development:} System Design (GeeksforGeeks), The Complete dbt Bootcamp (Udemy)

\end{document}
